The Calibration Reference Data System

### 2015-10-04 docs/paper/crds.tex
fixed a bunch of figure issues
git-svn-id: https://aeon.stsci.edu/ssb/svn/crds_server/trunk@2122 37088bc5-bd3f-4c5b-b9de-119bb1e8f7e3

xxx example 1 (highlighting a \& b)

\begin{figure*}
\centering
\begin{verbatim}
selector = Match({
    ('MIRIFULONG', 'FAST', 'FULL') : UseAfter({
        '2015-01-27 12:05:34' 'jwst_miri_dark_0029.fits',
        '2015-03-22 00:29:01' 'jwst_miri_dark_0032.fits',
        '2015-04-07 09:14:00' 'jwst_miri_dark_0047.fits',
        ...
        }),
    ('MIRIFUSHORT', 'SLOW', 'FULL') : UseAfter({
        '2015-01-25 12:06:34' 'jwst_miri_dark_0099.fits',
        '2015-03-21 00:28:01' 'jwst_miri_dark_0101.fits',
        '2015-04-08 09:13:00' 'jwst_miri_dark_0127.fits',
        ...
        }),
        ...
})
\end{verbatim}
\caption{xxx}
\end{figure*}

xxx example 2 adding c
\begin{figure}
\begin{verbatim}
selector = SelectVersion({
   '<3.1':    'jwst_miri_flat_0065.fits',
   '<5':      'jwst_miri_flat_0073.fits',
   'default': 'jwst_miri_flat_123.fits',
})
\end{verbatim}
\end{figure}

xxx example 3 illustrating d

\begin{figure}
\begin{verbatim}
selector = Bracket({
    1.2: "cref_flatfield_120.fits",
    1.5: "cref_flatfield_124.fits",
    5.0: "cref_flatfield_137.fits",
})
\end{verbatim}
\end{figure}

Here, a parameter value of 1.3 returns the value:

\begin{verbatim}
('cref_flatfield_120.fits', 'cref_flatfield_124.fits')
\end{verbatim}

xxxx example 4 illustrating e

\begin{verbatim}
selector = Match({
    ('WFC', 'N/A', 'BETWEEN 1220 1530', 'FR782N') :  "hst_wfc3_flatfile_0027.fits",
    ('WFC', 'N/A', 'BETWEEN 1530 1690', 'FR782N') :  "hst_wfc3_flatfile_0028.fits",
    ...
})
\end{verbatim}

Here a wavelength of 1300 (between 1220 and 1530) results in the partial match
of

\begin{verbatim}
'hst_wfc3_flatfile_0027.fits' and eliminates 
"hst_wfc3_flatfile_0028.fits"
\end{verbatim}

as a candidate.   Since BETWEEN can be used in an arbitrary Match parameter
slot,  potentially multiple times,  volumes can be described, and also
described in concert with other types of match syntax for other parameters
such as wildcard matching or regular expressions.

XXXXXXX I think the capabilities of (e) are actually folded into Match()
described in (a),  where each individual parameter of a match case can use
one of several match syntaxes.   Further,  there is no requirement that the
match expressions of the same parameter use the same method across all cases,
and indeed it is common to use N/A which is a specialized kind of match.

\begin{verbatim}
XXXX I documented all this stuff here:

XXXX   https://jwst-crds.stsci.edu/static/users_guide/rmap_syntax.html#selectors
\end{verbatim}

XXXX By far the most common match syntax used is the literal-value-or-glob,
including the degenerate case of a single literal value.  Unlike CDBS which had
discrete rows for every combination of discrete parameter values, CRDS
summarizes the combinatorial explosion of parameter possibilities into a single
concise multi-parameter expression by virtue of the matching syntax.  It is far
more comprehensible to look at one multi-parameter match expression with
or-globs than it is to scan 60 or 100 simple rows in the CDBS database.
Another common match expression is N/A.  BETWEEN has also been used.

@@

xxx example of instrument context file

@@

xxx example of pipeline context file

@@

The machinery for submitting reference files is an interactive web-based
system. The ability to submit files or make changes requires user
validation. Figure xxx shows a screen shot of the home page of the CRDS
system, which is visible to the public. The submission capabilities 
are indicated in the xxx links in
xxx. Figure xxx shows the submission web page for updates for reference
files. This examples is for xxx.

\begin{figure*}[ht!]
\centering
\includegraphics[width=180mm]{JWST_Public_Home_Page.png}
\caption{JWST CRDS Public Home Page}
\end{figure*}

\begin{figure*}[ht!]
\centering
\includegraphics[width=180mm]{JWST_Authenticated_Home.png}
\caption{JWST CRDS Authenticated User Home Page}
\end{figure*}

\begin{figure*}[ht!]
\centering
\includegraphics[width=180mm]{JWST_Batch_File_Submission.png}
\caption{JWST Batch File Submission Page}
\end{figure*}

\begin{figure*}[ht!]
\centering
\includegraphics[width=180mm]{JWST_Good_Submission_Review_Page_(after_confirmation).png}
\caption{JWST Good Submission Example}
\end{figure*}

\begin{figure*}[ht!]
\centering
\includegraphics[width=180mm]{JWST_Failed_Submission_DM_schema_violation.png}
\caption{JWST failed submission example}
\end{figure*}

\begin{figure*}[ht!]
\centering
\includegraphics[width=180mm]{JWST_Submission_Confirmed.png}
\caption{JWST submission confirmed example}
\end{figure*}

File submission is limited to authenticated users. The fully automatic
standard process is dubbed "Batch Reference
Submission" in reference to submission of a pile of files for one instrument,
multiple types,  and automatic certification and rules updates.

>>>>

Figure~\ref{fig:example1} illustrates use of the first two items. Essentially two different configurations are supported, and for each there are three possible choices of reference files that depend on the date of the observation. For example, if the date of the observation for the configuration {\tt (\textquotesingle MIRIFULONG\textquotesingle , \textquotesingle FAST\textquotesingle , \textquotesingle FULL\textquotesingle )} is 2015-04-02, the second choice will be used resulting in the return of {\tt jwst\_miri\_dark\_0032.fits} as the recommended reference file.

\begin{figure*}
\begin{verbatim}
selector = Match({
    ('MIRIFULONG', 'FAST', 'FULL') : UseAfter({
        '2015-01-27 12:05:34' 'jwst_miri_dark_0029.fits',
        '2015-03-22 00:29:01' 'jwst_miri_dark_0032.fits',
        '2015-04-07 09:14:00' 'jwst_miri_dark_0047.fits',
        ...
        }),
    ('MIRIFUSHORT', 'SLOW', 'FULL') : UseAfter({
        '2015-01-25 12:06:34' 'jwst_miri_dark_0099.fits',
        '2015-03-21 00:28:01' 'jwst_miri_dark_0101.fits',
        '2015-04-08 09:13:00' 'jwst_miri_dark_0127.fits',
        ...
        }),
        ...
})
\end{verbatim}
\caption{Example showing basic parameter matching rules coupled with date dependency.}
\label{fig:example1}
\end{figure*}

Figure~\ref{fig:example2} shows the use of the software selection mechanism. In this case if the software version is less than 3.1 (using the typical version semantics) then the first file will be chosen, if less than 5 the second will be chosen, otherwise the last file will be used.

\begin{figure*}
\begin{verbatim}
selector = SelectVersion({
   '<3.1':    'jwst_miri_flat_0065.fits',
   '<5':      'jwst_miri_flat_0073.fits',
   'default': 'jwst_miri_flat_123.fits',
})
\end{verbatim}
\caption{Example showing use of the software version selection mechanism.}
\label{fig:example2}
\end{figure*}

Figure~\ref{fig:example3} shows how two reference files may be selected
that bracket the particular parameter. Here if the parameter has a value 
of 3.2, then the pair of images 
(\texttt{cref\_flatfield\_124.fits}, \texttt{cref\_flatfield\_137.fits}) will be returned

\begin{figure*}
\begin{verbatim}
selector = Bracket({
    1.2: "cref_flatfield_120.fits",
    1.5: "cref_flatfield_124.fits",
    5.0: "cref_flatfield_137.fits",
})
\end{verbatim}
\caption{Example showing bracketing selection.}
\label{fig:example3}
\end{figure*}

Figure~\ref{fig:example4} shows how a
wavelength of 1300 (between 1220 and 1530) results in the partial match 
of \texttt{hst\_wfc3\_flatfile\_0027.fits} and eliminates 
\texttt{hst\_wfc3\_flatfile\_0028.fits}
of as a candidate.   Since \texttt{BETWEEN}
can be used in an arbitrary Match parameter
slot,  potentially multiple times,  volumes can be described, and also
described in concert with other types of match syntax for other parameters
such as wildcard matching or regular expressions.

\begin{figure*}
\begin{verbatim}
selector = Match({
    ('WFC', 'N/A', 'BETWEEN 1220 1530', 'FR782N') :  "hst_wfc3_flatfile_0027.fits",
    ('WFC', 'N/A', 'BETWEEN 1530 1690', 'FR782N') :  "hst_wfc3_flatfile_0028.fits",
    ...
})
\end{verbatim}
\caption{An example showing matching specified ranges.}
\label{fig:example4}
\end{figure*}

[xxx need headers included and explained since examples have unnamed
parameters that won't make any sense unless put in context]

[xxx insert full description of syntax used]

[xxx somewhere put in explanation of safety features preventing hand
mangling of rules files and configuration]

Full documentation of the syntax and semantics of all the rmap and
context files is available on the web 
\footnote{\texttt{https://jwst-crds.stsci.edu/static/users\_guide/rmap\_syntax.html\#selectors}}

@@

[xxx need example of instrument context file]

@@

[xxx need example of pipeline context file]

@@

The machinery for submitting reference files is an interactive web-based
system. The ability to submit files or make changes requires user
validation. Figure~\ref{fig:publichome} 
shows a screen shot of the home page of the CRDS
system, which is visible to the public.

File submission is limited to authenticated users. The home page for
authentic pages is shown in Figure~\ref{fig:authenticatedhome}.
The fully automatic
standard process is dubbed ``Batch Reference Submission'' 
in reference to submission of a pile of files for one instrument,
multiple types,  and automatic certification and rules updates.

Figure~\ref{fig:batchsubmission} shows the starting page for submitting
a batch set of files using the streamlined system.

Figure~\ref{fig:goodsubmissionreview} shows the results of a successfully validated batch  submission request.

Figure~\ref{fig:failedsubmission} shows the results of an unsuccessfully validated batch submission request showing what went wrong.

Figure~\ref{fig:confirmedsubmission} shows the results of a successfully completed submission request.

\begin{figure*}[ht!]
\centering
\includegraphics[width=180mm]{JWST_Public_Home_Page.png}
\caption{JWST CRDS Public Home Page}
\label{fig:publichome}
\end{figure*}

\begin{figure*}[ht!]
\centering
\includegraphics[width=180mm]{JWST_Authenticated_Home.png}
\caption{JWST Authenticated Users Home Page}
\label{fig:authenticatedhome}
\end{figure*}

\begin{figure*}[ht!]
\centering
\includegraphics[width=180mm]{JWST_Batch_File_Submission.png}
\caption{JWST Batch File Submission Page}
\label{fig:batchsubmission}
\end{figure*}

\begin{figure*}[ht!]
\centering
\includegraphics[width=180mm]{JWST_Good_Submission_Review_Page_(after_confirmation).png}
\caption{JWST Good Submission Example}
\label{fig:goodsubmissionreview}
\end{figure*}

\begin{figure*}[ht!]
\centering
\includegraphics[width=180mm]{JWST_Failed_Submission_DM_schema_violation.png}
\caption{JWST failed submission example}
\label{fig:failedsubmission}
\end{figure*}

\begin{figure*}[ht!]
\centering
\includegraphics[width=180mm]{JWST_Submission_Confirmed.png}
\caption{JWST submission confirmed example}
\label{fig:confirmedsubmission}
\end{figure*}
